Statically Typed String Sanitation Inside a Python

### 2014-10-07 sanitation-psp14/final.tex
remove -short files and added final.pdf

\begin{defn}[Definition of \lhead{r}]
The function $\lhead{r}$ is defined in terms of the structure of $r$:
\begin{itemize}[noitemsep]
\item $\lhead{a r'} = a$ where $a \in \Sigma$
\item $\lhead{r_1r_2} = \lhead{r_1}$
\item $\lhead{\epsilon} = \epsilon$
\item $\lhead{r_1 +  r_2}  = \lhead{r_1} + \lhead{r_2}$
\item $\lhead{r*} = \epsilon + \lhead{r}$
\item $\lhead{.} = a_1 + a_2 + ... + a_n$ for all $a_i \in \Sigma$ where $|\Sigma| = n$.
\end{itemize}
\end{defn}

@@

\section{Acknowledgements}
This work was supported by supported by the National Security Agency
lablet contract \#H98230-14-C-0140
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END SECTION TWO -- THIS IS THE CONFLICT LINE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{defn}[Definition of \lhead{r}]
The relation $\lhead{r}=r'$ is defined in terms of the structure of $r$:
\begin{itemize}[noitemsep]
\item $\lhead{\epsilon} = \epsilon$
\item $\lhead{.} = a_1 + a_2 + ... + a_n$ for all $a_i \in \Sigma$ where $|\Sigma| = n$.
\item $\lhead{a} = a$ %where $a \in \Sigma$
\item $\lhead{r_1\cdot r_2} = \lhead{r_1}$
\item $\lhead{r_1 +  r_2}  = \lhead{r_1} + \lhead{r_2}$
\item $\lhead{r*} = \epsilon + \lhead{r}$
\end{itemize}
\end{defn}

@@

\section{Acknowledgements}
This work was supported by supported by the National Security Agency
lablet contract \#H98230-14-C-0140.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END SECTION TWO -- THIS IS THE CONFLICT LINE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
